\LARGE \bf Planning with Attitude

### 2020-12-28 paper/main.tex
Clean out old files
Update Wahba problem

% Plotting
\usepackage{pgfplots}
\pgfplotsset{compat=1.15,
	legend style={font=\footnotesize},
}
\usepackage{tikzscale}
% \pgfplotsset{every axis plot post/.style={
%     very thick,
% }
% }

@@

\newcommand{\todo}[1]{\textcolor{red}{TODO: #1}}

@@

    \subsection{Unit Quaternions} \label{sec:quaternions}
        We leverage the fact that quaternions are linear operators and that the space of
        quaternions $\mathbb{H}$ is isomorphic to $\R^4$ to explicitly
        represent---following the Hamilton convention---a quaternion $\q \in \mathbb{H}$
        as a standard vector $q \in \R^4 := [q_s \;\; q_v^T]^T$ where $q_s \in \R$ and
        $q_v \in \R^3$ are referred to as the scalar and vector parts of the quaternion,
        respectively. The space of unit quaternions, $\Q = \{q : \norm{q}_2 = 1\}$, is a 
        a double-cover of the rotation group $SO(3)$, since $q$ and $-q$ represent the same 
        rotation \cite{markley2014fundamentals}.

@@

    \subsection{Results}
    Figure \ref{fig:wahba_convergence} compares the multiplicative Gauss-Newton method
    with a na\"ive Newton's method in which the quaternion is simply projected back onto
    the unit sphere at every iteration. The na\"ive method makes progress initially, but
    quickly stalls. By correctly handling the group structure of unit quaternions, the
    multiplicative method is able to maintain the fast convergence rates typical of
    Newton's method.
    \begin{figure}

        \centering
        \includegraphics[width=\columnwidth, height=5cm]{figures/wahba_convergence.tikz}
        \caption{Convergence comparison for Wahba's problem. By modfying Newton's method
        with the methods of section \ref{sec:Quaternion_Calculus}, quadratic convergence
        rates are achieved, while a na\"ive approach stalls after only a few
        iterations.}
        \label{fig:wahba_convergence}
    \end{figure}

>>>>

% Plotting
\usepackage{pgfplots}
\pgfplotsset{compat=1.15,
	legend style={font=\footnotesize},
}
\usepackage{tikzscale}
\usepgfplotslibrary{fillbetween}
% \pgfplotsset{every axis plot post/.style={
%     very thick,
% }
% }

@@

\newcommand{\todo}[1]{\textcolor{red}{TODO: #1}}
\newcommand{\added}[1]{\textcolor{blue}{#1}}

@@

    \subsection{Unit Quaternions} \label{sec:quaternions}
        We leverage the fact that quaternions are linear operators and that the space of
        quaternions $\mathbb{H}$ is isomorphic to $\R^4$ to explicitly
        represent---following the Hamilton convention---a quaternion $\q \in \mathbb{H}$
        as a standard vector $q \in \R^4 := [q_s \;\; q_v^T]^T$ where $q_s \in \R$ and
        $q_v \in \R^3$ are referred to as the scalar and vector parts of the quaternion,
        respectively. The space of unit quaternions, $\Q = \{q : \norm{q}_2 = 1\}$, is a 
        double-cover of the rotation group $SO(3)$, since $q$ and $-q$ represent the same 
        rotation \cite{markley2014fundamentals}.

@@

    \subsection{Results}
    Figure \ref{fig:wahba_convergence} compares the multiplicative Gauss-Newton method
    with a na\"ive Newton's method in which the quaternion is simply projected back onto
    the unit sphere at every iteration. The na\"ive method makes progress initially, but
    quickly stalls. By correctly handling the group structure of unit quaternions, the
    multiplicative method is able to maintain the fast convergence rates typical of
    Newton's method. \added{By comparing our method with the global solution obtained
    from an SVD decomposition, we see that our method recovers the globally optimal
    solution within a small number of iterations.}
    \begin{figure}

        \centering
        \includegraphics[width=\columnwidth, height=5cm]{figures/wahba_convergence.tikz}
        \caption{Convergence comparison for Wahba's problem. \added{The error
        is the angle between the current solution and the globally optimal
        solution computed using SVD decomposition \todo{Kevin: add citation}.
        The thick line is the average result of 100 trials with randomized
        orientations and measurements. The thin lines are the maximum and
        minimum over all 100 trials.} By modfying Newton's method with the
        methods of section \ref{sec:Quaternion_Calculus}, quadratic
        convergence rates are achieved, while a na\"ive approach stalls after
        only a few iterations.}
        \label{fig:wahba_convergence}
    \end{figure}
